\section{Gameplay}

The game has only command line interface. It starts with a text greeting the
user. At any time during the game, the user can obtain a list of allowed
commands via \textsf{allow}. As an example, just after fresh start the
following is shown.
\begin{verbatim}
 > allow
 Allowed commands are allow, exit, help, play.
\end{verbatim}

To start standard game against computer, type in the following.
\begin{verbatim}
play local
game standard
hi
ai
\end{verbatim}

Once the game is created and the board is shown, active player can proceed and
there are several possibilities how. The user could exit the game by typing in
\textsf{exit}. The user could ask an advice from a chosen heuristic,
\textsf{advise negamax}. At the moment, only \textsf{rnd} (random choice) and
\textsf{negamax} are implemented. To obtain current statistics type in
\textsf{show board $\mid$ players $\mid$ moves $\mid$ game}.
\begin{verbatim}
 > show board

 7   g m e l e c z
 6   p p p p p p p
 5   - - - - - - -
 4   + + + + + + +
 3   - - - - - - -
 2   P P P P P P P
 1   G M E L E C Z

 /   a b c d e f g

 > show players

 * white 2E 1Z 1G 1C 7P 0S 1L 1M
   black 2e 1z 1g 1c 7p 0s 1l 1m

 > show moves

 (a2,a3) (a2,b3) (b2,a3) (b2,b3) (b2,c3)
 (c2,b3) (c2,c3) (c2,d3) (d2,c3) (d2,d3)
 (d2,e3) (e2,d3) (e2,e3) (e2,f3) (f2,e3)
 (f2,f3) (f2,g3) (g2,f3) (g2,g3) (a1,a3)
 (a1,c3) (c1,c3) (e1,e3) (g1,f3)
\end{verbatim}

To move, the user simply types in \textsf{move} command, for example
\textsf{move a1 c3}.

\vspace{0.5em}

If the user attempts to do unsupported actions, the program properly informs
the user.

\vspace{0.5em}

The game can also be constructed from a string representing custom FEN-ish
format. It describes each square rank-by-rank, then types of the players (ai
or hi), a color of the active player and, finally, information if monkey jump
currently happens. If monkey jump does not happen, then the last field is
$-1$. Otherwise, there should be a square address, from which monkey started
its jump. This will be used for deciding whether monkey is drown or not, if it
interrupts the jump being on a river square.
\begin{verbatim}
gmelecz/ppppppp/7/7/7/PPPPPPP/GMELECZ/h/a/w/-1
\end{verbatim}

To start non-standard game, type in only two following rows after the greeting
text is shown.
\begin{verbatim}
play local
game <fen string>
\end{verbatim}

Such strings will be used for game (de-)serialization later as the project
develops.
