\section{Rules}

There are two competing players in the game, black and white. Players alternate
turns, passing is not possible.

\vspace{0.5em}

\underline{\textbf{[L]ion}} is the King of the Jungle. It may not leave castle
around it. Inside castle, it moves and captures as the King in Chess. If there
is a vertical or diagonal line with no pieces between the two lions, the lion
may jump to the other lion and capture it.

\vspace{0.5em}

\underline{\textbf{[Z]ebra}} moves as the Knight in classic chess.

\vspace{0.5em}

\underline{\textbf{[E]lephant}} moves one or two squares in the horizontal or
vertical direction. It may jump over the nearest square (also river) and
capture the piece on the next square.

\vspace{0.5em}

\underline{\textbf{[G]iraffe}} moves without capture one step in any direction
(as the chess King). It can move or capture two steps away in any direction in
a straight line.

\vspace{0.5em}

\underline{\textbf{[C]rocodile}} moves as the King in Chess when on land.
Outside the river it can move straight towards the river (including the river
square) as a rook. Inside the river it move to another river square as a rook.
A crocodile \textbf{cannot} drown.

\vspace{0.5em}

\underline{\textbf{[P]awn}} moves and captures both straight and diagonally
forward. Being on the other side of the river, a~pawn may also move one or two
squares straight back, without the right to capture or jump. If a~pawn moves
to the last row, it is promoted to a~superpawn.

\vspace{0.5em}

\underline{\textbf{[S]uperpawn}} has the additional powers of moving and
capturing one square straight sideways and going one or two square straight
backwards or diagonally backward. When going backwards, it may neither capture
nor jump. A superpawns right to go backwards does not depend on its position:
they may go backwards at both sides and on the river.

\vspace{0.5em}

\underline{\textbf{[M]onkey}} moves as the King in Chess while not capturing.
It captures a piece by jumping over it in any direction to the square
immediately beyond, which must be vacant. A monkey may capture multiple pieces
in the same turn, but is not obliged to do so. Monkey jump can be interrupted
at any time. Once a monkey jumped over a piece, the piece immediately
disappears. If a monkey starts multiple capture being at a river square and
ends at any river square, it immediately drowns. If a monkey starts its jump
on the ground and ends in the river or opposite, it is not drown. Captures
before drowning are legal. The monkey captured opponent's Lion terminates the
move and the game.

\vspace{0.5em}

The object of the game is to win by capturing opponent's Lion as there is only
one King of the Jungle. The game immediately ends when a lion has been
captured. There is no check in Congo, so a lion may move to an attacked
square. Consequently, Congo has no draw by stalemate.
