\section{Algorithms}

\subsection{Alpha-beta negamax}

Please, refer to \textsf{Congo.Core.Algorithm.cs} for implementation details.

\vspace{0.5em}

In original Minimax algorithm, one of the players (white) maximizes, another
(black) minimizes. Score is calculated with respect to both players. The value
could be either +high, 0 or --low. For white player, the higher score is the
better. On the contrary, for black the lower score is the better.

\vspace{0.5em}

\textbf{Negamax, leaf node}

\vspace{0.5em}

This paragraph describes how board score is determined and passed within
decision tree with respect to Minimax algorithm. Negamax deals with both
players equally, both maximize. To achieve such behavior we should properly
adjust score at the leaf node and pass obtained score in a specific way.

\vspace{0.5em}

Lets proceed with example. Suppose evaluation function returns +1 if white
player wins, --1 if black player wins, otherwise 0. White player checks
winning move and calls negamax with deep 0. Black player recognize that the
game is over and returns +1. White player goes through all returned values and
takes maximum value +1 if it appears.

\vspace{0.5em}

Next situation, the same evaluation function, but black player checks winning
move and neutral move (neither winning nor loosing) and calls negamax. For the
first move the board is evaluated to --1, and for the second to 0. Maximum of
two values is 0, so black would skip the best option if miximizes. We should
have inverted obtained score at the leaf node before the value is returned.
Then 0 becomes 0, but --1 becomes +1. Smaller values at the leaf nodes become
larger values when returned!

\vspace{0.5em}

All in all, black active player (or white opponent) at a terminal node returns
+score, white active player (or black opponent) at a terminal node returns
--score.

\vspace{0.5em}

\textbf{Negamax, internal node}

\vspace{0.5em}

Suppose, there is a white player from the previous paragraph. It found winning
move at the leaf node. Let black player be above white player within the
decision tree. If white player returns +1 (maximum possible value) and black
maximizes, then black would choose worst possible value and eventually move.
The best values returned from nodes below should be represented as the worsest
values for the opponent. Therefore, before value is returned, it should be
inverted (* --1), so that the player above could maximize.

\vspace{0.5em}

\textbf{Alpha-beta pruning}

